---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Temporal resolution of hydrogen peroxide (H2O2) dynamics during heat stress do not support a causative role in coral bleaching

The goal of this project is to reproduce all analyses and figures of the paper

> Title: Temporal resolution of hydrogen peroxide (H2O2) dynamics during heat stress do not support a causative role in coral bleaching
> 
> Authors: Schlotheuber M, Voolstra CR, de Beer D, Camp EF, Klatt JM, Ghilardi M, Neumüller K, Ousley S, Bejarano S

currently under revision at Coral Reefs.

## Content

This repository is structured as follow:

- [:file_folder:data/](https://github.com/MarlenSchlotheuber/CBASS_Microsensor_ROS/tree/CBASS_Microsensor_ROS/data): contains all raw and processed data and images used for Visual Bleaching Assessment (VBA).
- [:file_folder:R/](https://github.com/MarlenSchlotheuber/CBASS_Microsensor_ROS/tree/CBASS_Microsensor_ROS/R): contains all the R code used to reproduce analyses and figures.
- [:file_folder:figures/](https://github.com/MarlenSchlotheuber/CBASS_Microsensor_ROS/tree/CBASS_Microsensor_ROS/figures): contains all figures created during the analyses.

## Instructions

- Clone this repository (for those not familiar with GitHub, click on the green button `Code` on the project main page on GitHub and then on `Download ZIP` to download the entire repository, thus unzip it).

- Open the `.Rproj` file in RStudio or open an R session with working directory set to the root of the project.

- Reproduce the entire project by running:

``` r
# Install dependencies
devtools::install_deps()
# Run all scripts
scripts <- list.files("R/")
lapply(paste("R", scripts, sep = "/"), source)
```
For questions related to the data please contact Marlen Schlotheuber at <marlen.schlotheuber@uni-konstanz.de>.
For questions related to the code please contact Mattia Ghilardi at <mattia.ghilardi91@gmail.com>.

## Working environment

```{r echo=FALSE}
sessionInfo()
```
